\section{Honors and Awards}

% New bullet point for the next sections
\renewcommand{\labelitemi}{o}

\cvline{2012 - 2015}{ 
        \begin{itemize}
            \item Top Academic Achievement, Class of 2015, \textit{Colegio Santa Sabina.}
        \end{itemize}
}
\cvline{2022}{ 
        \begin{itemize}
            \item M.Sc. Thesis Defense, awarded maximum distinction (7.0/7.0), \textit{Universidad de Concepción} (UdeC).
        \end{itemize}
}
\cvline{2025}{ 
        \begin{itemize}
            \item Sunbelt 2025 Student Award: an annual recognition for young scholars, \textit{International Network for Social Network Analysis} (INSNA).
        \end{itemize}
}

\subsection{\Large{Scholarships and Grants}}
\vspace{5pt}

\cvline{2016}{ 
        \begin{itemize}
            \item Enrique Molina Garmendia Scholarship Recipient, Class of 2016, \textit{Universidad de Concepción} (UdeC).
        \end{itemize}
}
\cvline{2023 - Present}{ 
        \begin{itemize}
            \item Grant: Beca Doctorado Nacional, \textit{Agencia Nacional de Investigación y Desarrollo} (ANID).
        \end{itemize}
}
\cvline{2025 - Present}{
        \begin{itemize}
            \item Grant: Beca Complementaria, Gastos Operacionales, with a score of 5.0 out of 5.0, \textit{Agencia Nacional de Investigación y Desarrollo} (ANID).
        \end{itemize}
}

\subsection{\Large{Grant Proposals}}
\vspace{5pt}

\cvline{2026, Submitted}{
        \begin{itemize}
            \item NIH R21 grant proposal, submitted June 16, 2026. PI: Thomas W. Valente; Co-PI: Andrés Colubri; Collaborators: George Vega Yon and Aníbal Olivera. \textit{[Title and details forthcoming]}.
        \end{itemize}
}

\section{Research and Academic Activities}
\vspace{5pt}

\subsection{\Large{Conferences}}
\vspace{5pt}

\cvline{2019, Attendee}{
        \begin{itemize}
            \item  Winter School HEP-PUC, Topics on Graviticulas, \textit{Pontificia Universidad Católica de Chile} (PUC).
        \end{itemize}
        }
\cvline{2019, Attendee}{
        \begin{itemize}
            \item  ${2}^{\text{nd}}$ UdeC School on CFT and String Theory, \textit{Universidad de Concepción} (UdeC).
        \end{itemize}
        }
\cvline{2022, Presenter}{
        \begin{itemize}
            \item  ${53}^{\text{rd}}$ Annual Meeting of the APS Division of Atomic, Molecular and Optical Physics. 
            \newline  
            \href{https://meetings.aps.org/Meeting/DAMOP22/Session/F01.106}{Online Poster: "Atom-atom van der Waals Interactions through a Lens".}
            \newline
            \textit{American Physical Society} (APS). 
        \end{itemize}
        }
\cvline{2024, Presenter}{
        \begin{itemize}
            \item  Computational Social Science 2024 Annual Conference, Santa Fe, NM, USA. 
            \newline \href{https://computationalsocialscience.org/conferences/css-2024-santa-fe/}{In-person Poster: "How does network structure in Agent-Based Models affect epidemiological parameters? A large simulation study".} 
            \newline
            \textit{Computational Social Science Society of the Americas}  (CSSSA).
        \end{itemize}
        }
\cvline{2025, Presenter}{
        \begin{itemize}
            \item  Sunbelt 2025, Paris, France. 
            \newline 
            \href{https://sunbelt2025.org/home-2-2/}{Oral Presentation: "Diffusion of Innovations with Individual Preferences: The Role of Social Reinforcement and Homophilic Ties".} 
            \newline
            \textit{International Network for Social Network Analysis} (INSNA).
        \end{itemize}
        }
\cvline{2025, Session Co-organizer}{
        \begin{itemize}
            \item  Sunbelt 2025, Paris, France. 
            \newline 
            \href{https://sunbelt2025.org/home-2-2/}{Session co-organized with Thomas Valente (USC): "Contagion and Diffusion processes through Social Networks".}
            \newline
            \textit{International Network for Social Network Analysis} (INSNA).
        \end{itemize}
        }
\cvline{2026, Presenter}{
        \begin{itemize}
            \item \href{https://snlab-cl.github.io/summerschool/}{2nd Chilean Summer School about Social Network Research, Santiago, Chile.}
            \newline
            \textit{Pontificia Universidad Católica de Chile} (PUC).
        \end{itemize}
        }
\cvline{2026, Presenter}{
        \begin{itemize}
            \item  NetSci 2026, Boston, MA, USA --- Satellite CPIN2 (Critical Phenomena in Networks).
            \newline
            Oral Presentation: "When Homophily governs the Criticality of Social Adoption".
            \newline
            \textit{Network Science Society} (NetSci).
        \end{itemize}
        }

\subsection{\Large{Talks}}
\vspace{5pt}        

\cvline{2024, Speaker}{
        \begin{itemize}
            \item  \textit{‘How does network structure in ABMs affect epidemiological parameters? A large simulation study’}, Epidemiological Division, Internal Medicine, University of Utah (UofU), Salt Lake City, Utah.
        \end{itemize}
        }
\cvline{2024, Speaker}{
        \begin{itemize}
            \item  \textit{‘New capabilities of netdiffuseR package: Multidiffusion models’}, Epidemiological Division, Internal Medicine, University of Utah (UofU), Salt Lake City, Utah.
        \end{itemize}
        }
\cvline{2024, Speaker}{
        \begin{itemize}
            \item  \textit{‘How does network structure in ABMs affect epidemiological parameters? A large simulation study’}, Center for Applied Network Analysis, University of Southern California (USC), Los Angeles, California.
        \end{itemize}
        }
\cvline{2024, Speaker}{
        \begin{itemize}
            \item  \textit{‘Social Contagion in Networks: Exploring Diffusion Dynamics and Research Insights’}, Research Center for Social Complexity, Universidad del Desarrollo (CICS), Santiago, Chile.
        \end{itemize}
        }
\cvline{2025, Speaker}{
        \begin{itemize}
            \item  \textit{‘Networks Decide for Us: When Networks Shape Behavior More Than Intentions.’}, Centro de Investigación en Complejidad Social, Universidad del Desarrollo (CICS), Santiago, Chile.
        \end{itemize}
        }
\cvline{2026, Speaker}{
        \begin{itemize}
            \item  \textit{‘Networks Decide for Us: When Networks Shape Behavior More Than Intentions.’}, III Jornada de Redes, Online.
        \end{itemize}
        }
\cvline{2026, Speaker}{
        \begin{itemize}
            \item  \textit{‘When Homophily governs the Criticality of Social Adoption’}, NetSci 2026 --- Satellite CPIN2 (Critical Phenomena in Networks), Boston, MA, USA.
        \end{itemize}
        }

\subsection{\Large{Workshops}}
\vspace{5pt}    
\cvline{2024, Instructor}{
        \begin{itemize}
            \item \href{usccana.github.io/netdiffuser-workshop/}{\textit{NetdiffuseR Workshop}}. Center for Applied Network Analysis, University of Southern California (USC), Los Angeles, California.
        \end{itemize}
        }
\cvline{2025, Instructor}{
        \begin{itemize}
            \item \href{https://github.com/USCCANA/netdiffuser-workshop}{\textit{Understanding Diffusion with netdiffuseR}}. Sunbelt 2025 (INSNA), Paris, France.
        \end{itemize}
        }
\cvline{2026, Instructor}{
        \begin{itemize}
            \item \href{https://policics.github.io/revisiting-surveys-workshop/0-index.html}{\textit{Revisiting Surveys: A view from Complexity Sciences}}. Summer School in Complex Systems 2026, Santiago, Chile.
        \end{itemize}
        }

\subsection{\Large{Publications}}
\vspace{5pt}

\cvline{2022}{
        \begin{itemize}
            \item  Olivera, A., Sinha, K., \& Solano, P., \textit{Dipole-dipole interactions through a lens}, Phys. Rev. A 106, 013703. \href{https://journals.aps.org/pra/abstract/10.1103/PhysRevA.106.013703}{doi.org/10.1103/PhysRevA.106.013703}.
        \end{itemize}
        }
\cvline{2024}{
        \begin{itemize}
            \item  Valente, T., Vega Yon, G., \& Olivera, A., \textit{A NetdiffuseR Tutorial: Estimating Network Influences on Behavior within the Diffusion Paradigm}, Connections. [available as Connections-D-25-00002-].
        \end{itemize}
        }
\cvline{2025}{
        \begin{itemize}
            \item  Vega Yon, G., Valente, T., \& Olivera, A., \textit{The netdiffuseR R package: Analysis of Diffusion and Contagion Processes on Networks}, Journal of Open Source Software. [Under review].
        \end{itemize}
        }
\cvline{2026}{
        \begin{itemize}
            \item  Fábrega, J., \& Olivera, A., \textit{Same Score, Different Network: Configuration-Level Heterogeneity in Composite Risk Measures}, Applied Network Science. [available at Research Square][https://doi.org/10.21203/rs.3.rs-8880036/v1].
        \end{itemize}
        }
\cvline{2026}{
        \begin{itemize}
            \item  Olivera, A., Fábrega, J., \& Valente, T.W.,\textit{Networks Decide for Us: Emergence of Adoption in Homophily-Imputed Social Topologies}. [available at Zenodo][https://doi.org/10.5281/zenodo.19360209].
        \end{itemize}
        }
\cvline{2026, Submitted}{
        \begin{itemize}
            \item  Olivera, A., Miljkovic, K., Cao, Y., Piombo, S., Barrington-Trimis, J., \& Valente, T.W. (corresponding author), \textit{E-cigarette Cessation as a Disadoption Process: Social Network Influences on Stable and Temporary Quitting}, Proceedings of the National Academy of Sciences (PNAS). [Submitted, June 2026; Manuscript \#2026-20751].
        \end{itemize}
        }
\cvline{Working}{
        \begin{itemize}
            \item  Olivera, A., \& Fábrega, J., \textit{Networked Influence in a Tabula Rasa Legislature: Tracing Co-authorship and Ideological Dynamics in the Chilean Constitutional Convention (2021-2022)}. [Working paper] [\href{https://github.com/aoliveram/Networked-Influence-Chilean-Constitutional-Convention}{github.com/aoliveram/Networked-Influence-Chilean-Constitutional-Convention}].
        \end{itemize}
        }

\subsection{\Large{Journal Reviewer}}
\vspace{5pt}

\cvline{2024}{
        \begin{itemize}
            \item Academic reviewer for the journal \textit{Social Networks}, Elsevier Editorial.
        \end{itemize}
        }

\subsection{\Large{Software Development}}
\vspace{5pt}

\cvline{2026}{
        \begin{itemize}
            \item  Vega Yon, G., Olivera, A., Valente, T. (2026). \textit{netdiffuseR: Analysis of Diffusion and Contagion Processes on Networks}. \href{https://cran.r-project.org/web/packages/netdiffuseR/index.html}{doi:10.5281/zenodo.1039317}, R package version 1.25.0, \href{https://github.com/USCCANA/netdiffuseR}{github.com/USCCANA/netdiffuseR}.
        \end{itemize}
        }

\subsection{\Large{Other Academic Activities}}
\vspace{5pt}

\cvline{2019, Speaker}{
        \begin{itemize}
            \item  Physics Forums, Title: \textit{Battle of Reality}. Aula Magna CFM, Universidad de Concepción (UdeC). 
        \end{itemize}
        }
\cvline{2022, Speaker}{
        \begin{itemize}
            \item  Science, Talks and Beer, Title: \textit{Anthology of Physics, a selection of eternal ideas}. Castillo Bar. 
        \end{itemize}
        }
\cvline{2025, Web Development}{
    \begin{itemize}
        \item Creation, design, and deployment of the official website of the Political Behavior Laboratory \textit{PoliCICS}. Center for Research in Social Complexity, Universidad del Desarrollo (UDD). Visit: \href{https://policics.github.io}{policics.github.io}.
    \end{itemize}
}