%\section{Otros}
%    \cvline{Movilidad}{Licencia de conducir, clase B.}

%===============================================================================
% STATEMENT OF NEED
%===============================================================================
\section{Statement of Need}

\vspace{0.5cm}

As a 27-year-old PhD student in Social Complexity Science at Universidad del Desarrollo in Santiago, Chile, my primary financial support comes from a national doctoral scholarship granted by the Chilean government (ANID), amounting to approximately 950 USD per month. A significant portion of this stipend (450 USD) is allocated to essential living costs, specifically rent, as I relocated from my hometown of Concepción to Santiago for my doctoral studies.

My personal savings were recently invested in a research visit to the United States to establish crucial academic collaborations. This visit was highly productive, enabling joint work with Dr. George Vega Yon (University of Utah) and Dr. Thomas Valente (University of Southern California). As a direct result of this collaboration, we have successfully organized the ``NetdiffuseR Workshop'' and a session on ``Contagion and Diffusion processes through Social Networks'' for the upcoming Sunbelt conference, where I am also scheduled to give an oral presentation on our research ``Diffusion of Innovations with Individual Preferences: The Role of Social Reinforcement and Homophilic Ties''.

Currently, I do not have any other specific financial support secured for attending the Sunbelt conference. My national scholarship is designated for living expenses within Chile and does not cover international travel or conference fees. Furthermore, institutional travel funding opportunities for PhD students at my university are extremely limited. Due to the recent expenditure of my savings on the foundational collaborative trip, I am facing significant financial uncertainty regarding my ability to attend Sunbelt.

Participation in Sunbelt is vital at this stage of my academic career. It represents a critical opportunity to present our collaborative work, receive feedback, engage directly with the international network science community, and build connections essential for my doctoral research and future prospects. Therefore, receiving this INSNA Travel Award is essential to make my attendance financially feasible.

\vspace{0.5cm}
%===============================================================================
% ESTIMATED BUDGET
%===============================================================================
\section{Estimated Budget for Sunbelt Conference Attendance}

\vspace{0.5cm}

\subsection{Conference Attendance Dates}
June 22nd to June 30th (9 days / 8 nights)

\vspace{0.5cm}

\subsection{Expected Costs}
\vspace{0.5cm}
\begin{itemize}
    \item \textbf{International Transportation:} Round-trip flight (\href{https://www.google.com/travel/flights/search?tfs=CBwQAhooEgoyMDI1LTA2LTIyagwIAhIIL20vMGRscXZyDAgDEggvbS8wNXF0ahooEgoyMDI1LTA2LTMwagwIAxIIL20vMDVxdGpyDAgCEggvbS8wZGxxdkABSAFwAYIBCwj___________8BmAEB}{Economy Class }), Santiago (SCL): \textbf{1200 USD}
    \item \textbf{Accommodation:} Low-budget lodging for 8 nights (Check-in June 22, Check-out June 30): \textbf{350 USD} \\
    \href{https://www.airbnb.cl/rooms/43672051?adults=1&check_in=2025-06-15&check_out=2025-06-23&search_mode=regular_search&source_impression_id=p3_1746108875_P3j1RylpBInPYmaA&previous_page_section_name=1000&federated_search_id=3869dce9-fdc6-437c-be28-d73b08091c33}{Airbnb link 1} \\
    \href{https://www.booking.com/hotel/fr/coffice-paris.es.html?label=es-cl-booking-desktop-LVoANQ22b9Q1GvFzlorfdQS652829001271%3Apl%3Ata%3Ap1%3Ap2%3Aac%3Aap%3Aneg%3Afi%3Atikwd-65526620%3Alp9198254%3Ali%3Adec%3Adm&aid=2311236&ucfs=1&checkin=2025-06-15&checkout=2025-06-23&dest_id=-1456928&dest_type=city&group_adults=1&no_rooms=1&group_children=0&nflt=price%3DCLP-min-100000-1&srpvid=26dd650ee78d026f&srepoch=1746109375&matching_block_id=479849501_285200522_1_0_0&atlas_src=sr_iw_title}{Booking link 2} \\
    \href{https://www.booking.com/hotel/fr/chez-mia-paris-paris.es.html?label=es-cl-booking-desktop-LVoANQ22b9Q1GvFzlorfdQS652829001271%3Apl%3Ata%3Ap1%3Ap2%3Aac%3Aap%3Aneg%3Afi%3Atikwd-65526620%3Alp9198254%3Ali%3Adec%3Adm&aid=2311236&ucfs=1&checkin=2025-06-15&checkout=2025-06-23&dest_id=-1456928&dest_type=city&group_adults=1&no_rooms=1&group_children=0&nflt=price%3DCLP-min-100000-1&srpvid=26dd650ee78d026f&srepoch=1746109375&matching_block_id=1258054601_410961765_0_0_0&atlas_src=sr_iw_title}{Booking link 3}
    \item \textbf{Conference Registration Fee:} (Student early-bird rate): \textbf{250} USD
    \item \textbf{Total Estimated Cost:} \textbf{1800} USD
\end{itemize}

\vspace{0.5cm}

\subsection{Funding Coverage}
\vspace{0.5cm}

\begin{itemize}
    \item \textbf{Amount covered by other sources:} Currently, \textbf{1300 USD}, mainly from my university. My national stipend covers living costs in Chile, and personal savings are depleted as detailed in the Statement of Need. I am actively seeking other funding, but none is confirmed.
    \item \textbf{Amount Requested from INSNA Travel Award:} \textbf{500} USD
\end{itemize}

\vspace{0.5cm}

